Essays in Computational Management Science

### 2018-05-21 Chapters/Chapter02.tex
Typos and Jamil's comments.

There is obviously a demand for use of SDM; but each group has been tied to their own \emph{ad-hoc} needs, and there has not been the emergence of a community centered on a tool. It is our belief that a tool such as standard open-source framework could bring orders of magnitude more researchers and attention if they were able to use the model, at zero cost, with an easy to use high-level language such as Python, in an intuitive platform such as Juypyter notebooks. Neuroscientists interested in long-term memory storage should not have to worry about high-bandwidth vector parallel computation.  This new tool would provide a ready to use system in which experiments could be executed almost as soon as designed --- and provide the needed replication of studies \citep{shen2014interactive}.

@@

>>>>

There is obviously a demand for use of SDM; but each group has been tied to their own \emph{ad-hoc} needs, and there has not been the emergence of a community centered on a tool. It is our belief that a tool such as standard open-source framework could bring orders of magnitude more researchers and attention if they were able to use the model, at zero cost, with an easy to use high-level language such as Python, in an intuitive platform such as Jupyter notebooks. Neuroscientists interested in long-term memory storage should not have to worry about high-bandwidth vector parallel computation.  This new tool would provide a ready to use system in which experiments could be executed almost as soon as designed --- and provide the needed replication of studies \citep{shen2014interactive}.

@@

% Jamil: De maneira geral, achei muito ensaístico e pouco "paper". Me parece que vai precisar de retrabalho para submissão se encarar um reviewer mais tradicional. Eu gostei, no entanto.
